\section*{Work Experience}
%
%
%
\subsection*{
  Graphic Designer / \href{https://www.linkedin.com/company/fintech-industrial/}{Fintech Industrial}
  \hspace*{\fill}
  \dateformat May 2021 -- Oct 2023
}
\begin{itemize}
  \item \textbf{Designed} the interface of the product to simplify complex financial data for a broad user base.
  \item \textbf{Created} multiple logo concepts, with the final logo used across branding.
  \item \textbf{Crafted} various digital assets, including brochures, email templates, and custom desktop wallpapers.
  \item \textbf{Documented} design sprints for handover to developers to ensure design consistency.
  \item Minor software development in React.js.
\end{itemize}
%
%
\subsection*{
  Product Designer / \href{https://bumbleboss.xyz/}{Freelance}
  \hspace*{\fill}
  \dateformat Nov 2017 -- Present
}
\begin{itemize}
  \item \textbf{Adapted} to diverse design guidelines, ensuring consistency and adherence across all\\projects while maintaining creativity.
  \item \textbf{Designed} for businesses in industries such as luxury, gaming studios, finance, and maritime, providing tailored solutions that meet each client's unique need
  \item \textbf{Created} custom animated logos and visual effects tailored to each project's specific requirements.
  \item \textbf{Skilled} in prototyping, delivering clear design workflows that bridge users, and developers.
  \item \textbf{Rebranded} existing designs, modernizing visuals to align with current industry standards.
\end{itemize}
%
%