\section*{Selected Work}
%
%
%
%
%
%
\subsection*{
	\href{https://bumbleboss.xyz/}{Personal Portfolio}
}
\subsubsection*{
	Tech: SCSS, Anime.js, Nuxt, Vue.js, TypeScript
	\hspace*{\fill}
	Winter 2023
}
My personal portfolio containing all my published professional work, documenting the
process behind each case.
\vspace{2mm}
\begin{tasks}
	\task Built and stylized the website to be very versatile and responsive with easy
	additions to avoid tech debt.
	\task Made use of Nuxt's state management to apply interactive interactions for
	the user.
	\task Added \href{https://content.nuxtjs.org/}{Nuxt Content} for document-driven
	capability of case studies.
\end{tasks}
%
%
%
%
\subsection*{
	\href{https://oklent.com/}{OKLENT Cloud Technologies}
}
\subsubsection*{
	Tech: HBS, SCSS, GSAP.js, Barba.js, Webpack
	\hspace*{\fill}
	Summer 2022
}
OKLENT is a start-up that deals with providing and implementing ERP systems
to small to medium-sized enterprises (SMEs).
\vspace{2mm}
\begin{tasks}
	\task Implemented a headless contact form using Webhooks to accomodate static
	site generation (SSG).
	\task Architected the website’s backend to use Markdown documents for
	specific routes for non-developers to modify content.
\end{tasks}
%
%
%
%
\subsection*{
	\href{https://bumbleboss.xyz/w/uk-circuit}{UK Circuit}
}
\subsubsection*{
	Tech: HBS, CSS3, Express.js, Node.js
	\hspace*{\fill}
	Spring 2020
}
The UK Circuit is a collection of FACEIT Hubs designed to increase the potential of the
UK \& Irish scene.
\begin{tasks}
	\task Developed a smart form that automatically fills in appropriate data based on
	user selection to get authentic and accurate reports.
	\task Built a dashboard for the moderators and userbase of UK Circuit to access and manage
	the submitted reports.
\end{tasks}
%
%
%
%
\subsection*{
	\href{https://bumbleboss.xyz/w/jockiemusic}{Jockie Music}
}
\subsubsection*{
	Tech: HBS, CSS3, Babel.js, Express.js, Node.js, Webpack
	\hspace*{\fill}
	Spring 2020
}
Te most feature-rich Discord music bot with support for sources such as Spotify,
Deezer, Tidal, Apple Music, Soundcloud and more.
\begin{tasks}
	\task Developed a smart form that automatically fills in appropriate data based on
	user selection to get authentic and accurate reports.
	\task Built a dashboard for the moderators and userbase of UK Circuit to access and manage
	the submitted reports.
\end{tasks}
