\section*{Projects}
%
%
%
\subsubsection*{
  Tech: SCSS, Anime.js, Nuxt, Vue.js, TypeScript
  \hspace*{\fill}
  All the time
}
\subsection*{
  \href{https://bumbleboss.xyz/}{Personal Portfolio}
}
My personal portfolio containing all my published professional work, documenting the process behind each case.
\smallskip
\begin{tasks}
  \task Built and stylized the website to be very versatile and responsive with easy additions to avoid tech debt.
  \task Made use of Nuxt's state management to apply interactive interactions for the user.
  \task Added \href{https://content.nuxtjs.org/}{Nuxt Content} for document-driven capability of case studies.
\end{tasks}
%
%
\medskip
\subsubsection*{
  Tech: HBS, SCSS, GSAP.js, Barba.js, Webpack
  \hspace*{\fill}
  Summer 2022
}
\subsection*{
  \href{https://oklent.com/}{OKLENT Cloud Technologies}
}
OKLENT is a start-up that deals with providing and implementing ERP systems to small to medium-sized enterprises (SMEs).\smallskip
\begin{tasks}
  \task Implemented a headless contact form using Webhooks to accommodate static site generation (SSG).
  \task Architected the website’s backend to use Markdown documents for specific routes for non-developers to modify content.
\end{tasks}
%
%
\medskip
\subsubsection*{
  Tech: HBS, CSS3, Express.js, Node.js
  \hspace*{\fill}
  Spring 2020
}
\subsection*{
  \href{https://bumbleboss.xyz/w/uk-circuit}{UK Circuit}
}
The UK Circuit is a collection of FACEIT Hubs designed to increase the potential of the UK \& Irish scene.
\begin{tasks}
  \task Developed a smart form that automatically fills in appropriate data based on user selection to get authentic and accurate reports.
  \task Built a dashboard for the moderators and userbase of UK Circuit to access and manage the submitted reports.
\end{tasks}
%
%
\medskip
\subsubsection*{
  Tech: HBS, CSS3, Babel.js, Express.js, Node.js, Webpack
  \hspace*{\fill}
  Spring 2020
}
\subsection*{
  \href{https://bumbleboss.xyz/w/jockiemusic}{Jockie Music}
}
Te most feature-rich Discord music bot with support for sources such as Spotify, Deezer, Tidal, Apple Music, Soundcloud and more.
\begin{tasks}
  \task Developed a FAQ page whereas recursive answers appear to answer whatever's needed within context.
  \task Statistics page for the bot with search ability via input fields or URL parameters, while maintaining connection between the two.
\end{tasks}